
\section{GPU Environment Routines}
\label{sec:gpuenv}

\subsection*{psb\_gpu\_init --- Initializes PSBLAS-GPU
  environment}
\addcontentsline{toc}{subsection}{psb\_gpu\_init}

\begin{minted}[breaklines=true]{fortran}
call psb_gpu_init(ctxt [, device])
\end{minted}

This subroutine initializes the PSBLAS-GPU  environment. 
\begin{description}
\item[Type:] Synchronous.
\item[\bf  On Entry ]
\item[device] ID of GPU device to attach to.\\
Scope: {\bf local}.\\
Type: {\bf optional}.\\
Intent: {\bf in}.\\
Specified as: an integer value. \
Default: use \fortinline|mod(iam,ngpu)| where \fortinline|iam| is the calling
process index and \fortinline|ngpu| is the total number of GPU devices
available on the current node. 
\end{description}


{\par\noindent\large\bfseries Notes}
\begin{enumerate}
\item A call to this routine must precede any other PSBLAS-GPU call. 
\end{enumerate}

\subsection*{psb\_gpu\_exit --- Exit from  PSBLAS-GPU
  environment}
\addcontentsline{toc}{subsection}{psb\_gpu\_exit}

\begin{minted}[breaklines=true]{fortran}
call psb_gpu_exit(ctxt)
\end{minted}

This subroutine exits from the  PSBLAS GPU context.
\begin{description}
\item[Type:] Synchronous.
\item[\bf  On Entry ]
\item[ctxt] the communication context identifying the virtual
  parallel machine.\\
Scope: {\bf global}.\\
Type: {\bf required}.\\
Intent: {\bf in}.\\
Specified as: an integer variable.
\end{description}




\subsection*{psb\_gpu\_DeviceSync ---  Synchronize GPU device}
\addcontentsline{toc}{subsection}{psb\_gpu\_DeviceSync}

\begin{minted}[breaklines=true]{fortran}
call psb_gpu_DeviceSync()
\end{minted}

This subroutine ensures that all previosly invoked kernels, i.e. all
invocation of GPU-side code, have completed.


\subsection*{psb\_gpu\_getDeviceCount }
\addcontentsline{toc}{subsection}{psb\_gpu\_getDeviceCount}

\begin{minted}[breaklines=true]{fortran}
ngpus =  psb_gpu_getDeviceCount()
\end{minted}

Get number of devices available on current computing node. 

\subsection*{psb\_gpu\_getDevice }
\addcontentsline{toc}{subsection}{psb\_gpu\_getDevice}

\begin{minted}[breaklines=true]{fortran}
ngpus =  psb_gpu_getDevice()
\end{minted}

Get  device in use by current process. 

\subsection*{psb\_gpu\_setDevice }
\addcontentsline{toc}{subsection}{psb\_gpu\_setDevice}

\begin{minted}[breaklines=true]{fortran}
info = psb_gpu_setDevice(dev)
\end{minted}

Set  device to be used  by current process. 

\subsection*{psb\_gpu\_DeviceHasUVA }
\addcontentsline{toc}{subsection}{psb\_gpu\_DeviceHasUVA}

\begin{minted}[breaklines=true]{fortran}
hasUva = psb_gpu_DeviceHasUVA()
\end{minted}

Returns true if device currently in use supports UVA (Unified Virtual Addressing).

\subsection*{psb\_gpu\_WarpSize }
\addcontentsline{toc}{subsection}{psb\_gpu\_WarpSize}

\begin{minted}[breaklines=true]{fortran}
nw = psb_gpu_WarpSize()
\end{minted}

Returns the warp size.


\subsection*{psb\_gpu\_MultiProcessors }
\addcontentsline{toc}{subsection}{psb\_gpu\_MultiProcessors}

\begin{minted}[breaklines=true]{fortran}
nmp = psb_gpu_MultiProcessors()
\end{minted}

Returns the number of multiprocessors in the GPU device.

\subsection*{psb\_gpu\_MaxThreadsPerMP }
\addcontentsline{toc}{subsection}{psb\_gpu\_MaxThreadsPerMP}

\begin{minted}[breaklines=true]{fortran}
nt = psb_gpu_MaxThreadsPerMP()
\end{minted}

Returns the maximum number of threads per multiprocessor. 


\subsection*{psb\_gpu\_MaxRegistersPerBlock }
\addcontentsline{toc}{subsection}{psb\_gpu\_MaxRegisterPerBlock}

\begin{minted}[breaklines=true]{fortran}
nr = psb_gpu_MaxRegistersPerBlock()
\end{minted}

Returns the maximum number of register per thread block. 


\subsection*{psb\_gpu\_MemoryClockRate }
\addcontentsline{toc}{subsection}{psb\_gpu\_MemoryClockRate}

\begin{minted}[breaklines=true]{fortran}
cl = psb_gpu_MemoryClockRate()
\end{minted}

Returns the memory clock rate in KHz, as an integer. 

\subsection*{psb\_gpu\_MemoryBusWidth }
\addcontentsline{toc}{subsection}{psb\_gpu\_MemoryBusWidth}

\begin{minted}[breaklines=true]{fortran}
nb = psb_gpu_MemoryBusWidth()
\end{minted}

Returns the memory bus width in bits.

\subsection*{psb\_gpu\_MemoryPeakBandwidth }
\addcontentsline{toc}{subsection}{psb\_gpu\_MemoryPeakBandwidth}

\begin{minted}[breaklines=true]{fortran}
bw = psb_gpu_MemoryPeakBandwidth()
\end{minted}

Returns the memory peak bandwidth in MB/s (real double precision).



